Convective heat transport in stratified atmospheres at low and high Mach number

### 2017-06-13 tex/nusselt_paper.tex
fixes a type in abstract

\begin{abstract}
%Convection in astrophysical systems is stratified and
%often occurs at high Rayleigh number (Ra) and low
%Mach number (Ma).
We study stratified convection in the context of 
plane-parallel, polytropically stratified atmospheres. 
We perform a suite of 2D and 3D simulations in which we vary the initial
superadiabaticity ($\epsilon$) and the Rayleigh number (Ra) at a set
initial density stratification, aspect
ratio, and Prandtl number.
We find that the Mach number (Ma) is a strong function of $\epsilon$
in both 2D and 3D simulations, and that it is a 
weak function of Ra in 2D.
Surprisingly, we find that the evolved heat transport, 
quantified by the Nusselt number (Nu),
follows scaling relationships similar to those found in the well-studied, 
incompressble Rayleigh-B\'{e}nard problem.
The scaling of evolved fluid properties (Nu, Reynolds number,
stratification) differs in the subsonic and supersonic regimes; 
aside from the sonic transition, the evolved fluid properties
of low and high Ma flows are nearly identical.  
Our limited 3D runs suggest that
evolved fluid properties behave similarly in 2D and 3D.
\end{abstract}
\maketitle

@@

Our diffusivities thus scale as
\begin{equation}
\chi_t \propto \sqrt{\frac{\epsilon}{\text{Pr}\cdot\text{Ra}_t}}, \qquad
\nu_t \propto \sqrt{\frac{\epsilon\cdot\text{Pr}}{\text{Ra}_t}},
\end{equation}
and for constant Pr = 1, as in this work, $\chi_t = \nu_t$.

@@

The variation of Nu with Ra is shown in 
Fig. \ref{fig:re_and_nu_v_ra}a.  We find that the Nu depends primarily
on Ra, not on $\epsilon$, except where dynamical regimes change.
In 2D and at low to moderate Ra, 
Nu $\appropto$ Ra$^{1/3}$ regardless of $\epsilon$,
reminiscent of scaling laws in classical \RB theory \cite{king&all2012}.
As the flow becomes supersonic,  Nu $\appropto$ Ra$^{1/5}$.
2D runs at $\text{Ra }\gtrsim 10^3$Ra$_{\text{crit}}$
and $\epsilon = 10^{-4}$ exhibit windy convective states.
In these runs, the system is in flux equilibrium only when
time averaged over roll states and windy states.
A long time average
over both of these states produces a flat flux profile which
can be sensibly analyzed, but the presence of these time-dependent states
makes it difficult to equilibrate these higher Ra cases.
It is also important to note that
the value of Nu is heavily dependent upon the specific thermodynamic
structures of the solution, as double roll states will transport
heat more efficiently than single roll states, and slight changes in
Ra can result in a simulation latching on to one solution or the other.
In our limited 3D runs, it appears that Nu $\appropto$ Ra$^{2/7}$, a classic scaling law
seen in RB studies \cite{johnston&doering2009}.

>>>>

\begin{abstract}
%Convection in astrophysical systems is stratified and
%often occurs at high Rayleigh number (Ra) and low
%Mach number (Ma).
We study stratified convection in the context of 
plane-parallel, polytropically stratified atmospheres. 
We perform a suite of 2D and 3D simulations in which we vary the initial
superadiabaticity ($\epsilon$) and the Rayleigh number (Ra) at a set
initial density stratification, aspect
ratio, and Prandtl number.
We find that the Mach number (Ma) is a strong function of $\epsilon$
in both 2D and 3D simulations, and that it is a 
weak function of Ra in 2D.
Surprisingly, we find that the evolved heat transport, 
quantified by the Nusselt number (Nu),
follows scaling relationships similar to those found in the well-studied, 
incompressible Rayleigh-B\'{e}nard problem.
The scaling of evolved fluid properties (Nu, Reynolds number,
stratification) differs in the subsonic and supersonic regimes; 
aside from the sonic transition, the evolved fluid properties
of low and high Ma flows are nearly identical.  
Our limited 3D runs suggest that
evolved fluid properties behave similarly in 2D and 3D.
\end{abstract}
\maketitle

@@

Our diffusivities thus scale as
\begin{equation}
\chi_t \propto \sqrt{\frac{\epsilon}{\text{Pr}\cdot\text{Ra}_t}}, \qquad
\nu_t \propto \sqrt{\frac{\epsilon\cdot\text{Pr}}{\text{Ra}_t}},
\end{equation}
and for constant Pr = 1, as in this work, $\chi_t = \nu_t$.
We carry out two experiments in this letter: one in which
we fix $\epsilon$ and vary Ra, thus increasing the diffusive
timescales, and a second in which we fix Ra and vary $\epsilon$,
thus...

@@

The variation of Nu with Ra is shown in 
Fig. \ref{fig:re_and_nu_v_ra}a.  We find that the Nu depends primarily
on Ra, not on $\epsilon$, except where dynamical regimes change.
In 2D and at low to moderate Ra, 
Nu $\appropto$ Ra$^{1/3}$ regardless of $\epsilon$,
reminiscent of scaling laws in \RB boundary layer theory 
\cite{grossman&lohse2000, ahlers&all2009}.
As the flow becomes supersonic,  Nu $\appropto$ Ra$^{1/5}$.
2D runs at $\text{Ra }\gtrsim 10^3$Ra$_{\text{crit}}$
and $\epsilon = 10^{-4}$ exhibit windy convective states.
In these runs, the system is in flux equilibrium only when
time averaged over roll states and windy states.
A long time average
over both of these states produces a flat flux profile which
can be sensibly analyzed, but the presence of these time-dependent states
makes it difficult to equilibrate these higher Ra cases.
It is also important to note that
the value of Nu is heavily dependent upon the specific thermodynamic
structures of the solution, as double roll states will transport
heat more efficiently than single roll states, and slight changes in
Ra can result in a simulation latching on to one solution or the other.
In our limited 3D runs, it appears that Nu $\appropto$ Ra$^{2/7}$, a classic scaling law
seen in RB studies \cite{johnston&doering2009}.
